---
title: "lm-v-rlm"
author: "Xing Xiong"
date: "2016Äê11ÔÂ27ÈÕ"
output: html_document
---


3.
First,we calculate the slope for each country using the linear regression model.
Here we will use funtion map and function unnest.The latter one is to get the slope for each country as there are several same slopes in each row.
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)
library(tidyverse)
library(tidyr)
library(broom)
library(MASS)
gap_nested <- gapminder %>% mutate(log_gdpPercap = log10(gdpPercap)) %>%
  group_by(continent, country) %>% nest()
glimpse(gap_nested)
```

```{r}
gap_lm <- function(df){
  lm(lifeExp  ~ log_gdpPercap, data = df)
  }
gap_nested <- gap_nested %>% 
  mutate(lm_fit = map(data, gap_lm))
gap_nested <- gap_nested %>% 
  mutate(slope = map(lm_fit, coef))
lmslope <- unnest(gap_nested, slope)
```


Then compute the slope using rlm function and then combine these two kinds of slopes.

```{r}
gap_rlm <- function(df){
  rlm(log_gdpPercap ~ lifeExp ,data = df)
}

gap_nested <- gap_nested %>% 
  mutate(rlm_fit = map(data, gap_rlm))
gap_nested <- gap_nested %>% 
  mutate(slope2 = map(rlm_fit, coef))

rlmslope <- unnest(gap_nested, slope2)
slopes <- unnest(gap_nested, slope, slope2)
```


Then Produce a plot of the slope estimates from lm versus the slope estimates from rlm. 
```{r}
slopes %>% ggplot(aes(slope, slope2)) +geom_line(aes(group = country)) + geom_smooth(color = "red") + facet_wrap(~continent)
```

Combine unnested data with gapminder to plot per capita GDP versus life expectency.

```{r}
slopes <- slopes %>% mutate(diff = abs(slope-slope2))

slopes <- filter(slopes,diff >= 0.01) 

gapminder$gdpPercap <-log10(gapminder$gdpPercap)
forplot<-left_join(gapminder, slopes)

forplot%>%ggplot(aes(lifeExp, gdpPercap, colour = country)) + geom_point() + ggtitle("per capita GDP versus life expectency")
